COVID-19 dataset strength

### 2020-06-22 covid_dataset_strength/covid_dataset_strength.Rmd
Dataset is awesome

```{r}
dna_evolution_rate_per_genome_per_year <- 26
```

@@

The first COVID-19 sequence (`https://www.ncbi.nlm.nih.gov/nuccore/NC_045512`)
was created in December 2019. Currenly, May 2020, 
is `r years_per_pandemic` years later.

@@

```{r}
n_sequences <- 4329
```

There are `r n_sequences` COVID-19 sequences (`https://nextstrain.org/ncov`).

@@

This chance we call it `r p_state_transition`.

Based upon simulations (see https://github.com/richelbilderbeek/bbbq_p_trans), we 
estimate `r p_state_transition`:

@@

@@

>>>>

![](nextstrain.png)
```{r}
dna_evolution_rate_per_genome_per_year <- 23.565
```

@@

The first COVID-19 sequence (`https://www.ncbi.nlm.nih.gov/nuccore/NC_045512`)
was created in December 2019. Currenly, June 2020, 
is `r years_per_pandemic` years later.

@@

![](gisaid.png)

```{r}
n_sequences <- 49790
```

There are `r n_sequences` COVID-19 sequences (`https://www.gisaid.org/`).

@@

@@

> This plot shows the chance of a state transition `p`,
> per haplotype, based on simulated data

@@

Based upon simulations (see https://github.com/richelbilderbeek/bbbq_p_trans), we 
estimated this chance at `p_state_transition`:
